---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009. Our reasearch question: Does sex of the participant seem to be a factor for any of the drugs?

#Graphical Analysis 
# South Carolina

We will subset the data by sex to see if the drug is sex specific.

##AIDs Results (Male)

```{r}
ScarolinaM <- filter(Scarolina, sex=="M")
barchartGC(~infected + group, data = ScarolinaM, type="percent")
```
Given the barchart, it seems more males who recieved the drug aquired AIDs (around 67%) than maleswho recieved the placebo (around 50%). 

##AIDs Results (Females)

```{r}
ScarolinaF <- filter(Scarolina, sex=="M")
barchartGC(~infected + group, data = ScarolinaF, type="percent")
```
Given the Barchart, it seems more females who recieved the drug aquired AIDs (around 67%) than females who recieved the placebo (around 50%).

##AIDs Results (Both)

```{r}
barchartGC(~infected + group, data=Scarolina, type = "percent")
```
Given the barchart, those who conteracted AIDs and were given the placebo was only slightly more (i.e the difference of about 2%) than those who contracted AIDs and were given the drug.

# Central Africa

We will subset the data by sex to see if the drug is sex specific.

##AIDs Results (Male)

```{r}
CentralAfricaM <- filter(cenAfrica, sex=="M")
barchartGC(~infected + group, data = CentralAfricaM, type="percent")
```
Given the barchart, it seems more males who recieved the palcebo aquired AIDs (around 50%) than males who recieved the drug (around 49%). 

##AIDs Results (Females)

```{r}
CentralAfricaF <- filter(cenAfrica, sex=="F")
barchartGC(~infected + group, data = CentralAfricaF, type="percent")
```
Given the Barchart, it seems more females who recieved the placebo aquired AIDs (around 55%) than females who recieved the drug (around 45%).

##AIDs Results (Both)

```{r}
barchartGC(~infected + group, data=cenAfrica, type = "percent")
```
Given the barchart, those who conteracted AIDs and were given the placebo (around 52%) was more than those who contracted AIDs and were given the drug (around 46%).

# Korea

We will subset the data by sex to see if the drug is sex specific.

##AIDs Results (Male)

```{r}
KoreaM <- filter(korea, sex=="M")
barchartGC(~infected + group, data = KoreaM, type="percent")
```
Given the barchart, it seems more males who recieved the palcebo aquired AIDs (over 60%) than males who recieved the drug (around 30%). 

##AIDs Results (Females)

```{r}
KoreaF <- filter(korea, sex=="F")
barchartGC(~infected + group, data = KoreaF, type="percent")
```
Given the Barchart, it seems more females who recieved the drug aquired AIDs (over 60%) than females who recieved the placebo (under 40%).

##AIDs Results (Both)

```{r}
barchartGC(~infected + group, data=korea, type = "percent")
```
Given the barchart, the percentage of poeple who conteracted AIDs and were given the placebo (over 50%) were greater than those who contracted AIDs and were given the drug (around 44%).

#Numerical Results
# South Carolina 

##Males

```{r}
ScarolinaM_Table <- xtabs(~infected + group, data = ScarolinaM)
rowPerc(ScarolinaM_Table)
```
More males (57.35%) that were infected with aids recieved the actual drug, than males who recieved the placebo. 

##Females

```{r}
ScarolinaF_Table <- xtabs(~infected + group, data = ScarolinaF)
rowPerc(ScarolinaF_Table)
```
More females (57.35%) contracted AIDs after being administered the drug. 

##Both

```{r}
Scarolina_Table <- xtabs(~infected + group, data = Scarolina)
rowPerc(Scarolina_Table)
```
Overall 50.04% of those who did not contracted AIDs where given the real drug, while 49.37% of those who caught AIDs where given the drug.

#Central Africa

##Males

```{r}
CentralAfricaM_Table <- xtabs(~infected + group, data = CentralAfricaM)
rowPerc(CentralAfricaM_Table)
```
More males (50.53%) that were infected with aids recieved the placebo, than males who recieved the drug (49.47%). 

##Females

```{r}
CentralAfricaF_Table <- xtabs(~infected + group, data = CentralAfricaF)
rowPerc(CentralAfricaF_Table)
```
More females (53.45%) contracted AIDs after being administered the placebo. Of the women administered the actual drug 50.17% did not contract AIDs. 

##Both

```{r}
CentralAfrica_Table <- xtabs(~infected + group, data = cenAfrica)
rowPerc(CentralAfrica_Table)
```
Overall about 50% (50.10% to be exact) who recieved the drug did not contract AIDs, but of those who were administered the placebo 49.90% remained free of AIDs. 

#Korea

##Males

```{r}
KoreaM_Table <- xtabs(~infected + group, data = KoreaM)
rowPerc(KoreaM_Table)
```
Only 32.68% of those that were infected with aids recieved the actual drug, which is far less than those recieved the placebo (67.32%). 

##Females

```{r}
KoreaF_Table <- xtabs(~infected + group, data = KoreaF)
rowPerc(KoreaF_Table)
```
More females (65.43%) contracted AIDs after being administered the drug. Only 34.57% of women on the placebo contracted AIDs. 

##Both

```{r}
Korea_Table <- xtabs(~infected + group, data = korea)
rowPerc(Korea_Table)
```
Overall most who recieved the drug did not contract AIDs (50.33%). 


# Inferential Conclusion 





