---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009. Our reasearch question: Does sex of the participant seem to be a factor for any of the drugs?


# South Carolina

We will subset the data by sex to see if the drug is sex specific.

##AIDs Results (Male)

```{r}
ScarolinaM <- filter(Scarolina, sex=="M")
barchartGC(~infected + group, data = ScarolinaM, type="percent")
```
Given the barchart, it seems males who recieved the drug aquired AIDs (around 67%) than maleswho recieved the placebo (around 50%). 

##AIDs Results (Females)

```{r}
ScarolinaF <- filter(Scarolina, sex=="M")
barchartGC(~infected + group, data = ScarolinaF, type="percent")
```
Given the Barchart, it seems females who recieved the drug aquired AIDs (around 67%) than females who recieved the placebo (around 50%).

##AIDs Results (Both)

```{r}
barchartGC(~infected + group, data=Scarolina, type = "percent")
```
Given the barchart, those who conteracted AIDs and were given the placebo was only slightly more (i.e the difference of about 2%) than those who contracted AIDs and were given the drug.

# Central Africa

We will subset the data by sex to see if the drug is sex specific.


# Korea

We will subset the data by sex to see if the drug is sex specific.


# Inferential Conclusion 





